---
title: "My First Presentation"
author: "Jamison R. Crawford, MPA"
date: "8/7/2019"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## My New Slide

Slide with title...

Other content...

***
### Slide without Title

## Slide with Subheadings

### Unordered Lists

* Unordered Item 1
* Unordered Item 2
* Unordered Item 3

### Ordered Lists

1. Ordered Item 1
2. Ordered Item 2
3. Ordered Item 3

## Formatted Text

Here are some *words in italics*.

Here are some **words in bold**.

<br>

This should be spaced with `<br>`. 

Cool, you can name variables with backticks, e.g. `mtcars$mpg`.

## Code Chunk Example I

No echo:

```{r}
print(mtcars)
```

## Code Chunk Example II

With echo:

```{r}
print(mtcars, echo=TRUE)
```

## Code Chunk Example III

Without preceding `##`:

```{r, comment=""}
mtcars
```

## Code Chunk Example IV

*Without* evaluation:

```{r eval=FALSE, echo=TRUE}
mean(mtcars$mpg)
```

*With* evaluation:

```{r, echo=TRUE}
mean(mtcars$mpg)
```

*With* evaluation but no preceding comment `##`:

```{r, echo=TRUE, comment=""}
mean(mtcars$mpg)
```

## A Visualization

```{r echo=FALSE, message=FALSE}
if(!require(ggplot2)){install.packages("ggplot2")}
if(!require(scales)){install.packages("scales")}
suppressPackageStartupMessages(library(ggplot2))
suppressPackageStartupMessages(library(scales))
```

```{r, fig.align='center'}
ggplot(diamonds, aes(x = carat, y = price, color = price)) +
  geom_point(alpha = 0.1) +
  theme_minimal() +
  labs(title = "Diamonds by carat, price",
       x = "Carat",
       y = "Price (USD)", 
       caption = "Source: Diamonds Dataset, Package 'ggplot2'") +
  scale_x_continuous(labels = number) +
  scale_y_continuous(labels = dollar)
```

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

